---
title: "Slay the Spire Run Tracker"
author: "Aditya Rao"
date: "2022-09-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
my_working_dir = "/Users/adityarao/personal_projects/sts_tracker"
setwd(my_working_dir)
library(rjson)
library(data.table)
library(ggplot2)
library(plotly)
```

## Transfer any new data

```{r}
source(file.path(my_working_dir,"run_downloader.R"))
```

## Load run files into R as JSONs

Filtering out these runs:
* Non ascension 20 runs
* Runs that ended before floor 6 (considering these not serious runs)
* Runs that were victorious but didn't defeat the heart

```{r}
storage_dir = file.path(my_working_dir,"all_run_history/")

#make list of all valid ironclad runs
ironclad_list = list()
ironclad_files = list.files(file.path(storage_dir,"IRONCLAD"),full.names=T)
for(fn in ironclad_files){
  result = fromJSON(file = fn)
  if(result$ascension_level == 20 && result$floor_reached >= 6){
    if(!(result$victory == TRUE && result$floor_reached < 52)){
      ironclad_list[result$play_id] = list(result)
    }
  }
}
cat(sprintf("%s total Ironclad runs\n",length(ironclad_list)))

#make list of all valid silent runs
silent_list = list()
silent_files = list.files(file.path(storage_dir,"THE_SILENT"),full.names=T)
for(fn in silent_files){
  result = fromJSON(file = fn)
  if(result$ascension_level == 20 && result$floor_reached >= 6){
    if(!(result$victory == TRUE && result$floor_reached < 52)){
      silent_list[result$play_id] = list(result)
    }
  }
}
cat(sprintf("%s total Silent runs\n",length(silent_list)))

#make list of all valid defect runs
defect_list = list()
defect_files = list.files(file.path(storage_dir,"DEFECT"),full.names=T)
for(fn in defect_files){
  result = fromJSON(file = fn)
  if(result$ascension_level == 20 && result$floor_reached >= 6){
    if(!(result$victory == TRUE && result$floor_reached < 52)){
      defect_list[result$play_id] = list(result)
    }
  }
}
cat(sprintf("%s total Defect runs\n",length(defect_list)))

#make list of all valid watcher runs
watcher_list = list()
watcher_files = list.files(file.path(storage_dir,"WATCHER"),full.names=T)
for(fn in watcher_files){
  result = fromJSON(file = fn)
  if(result$ascension_level == 20 && result$floor_reached >= 6){
    if(!(result$victory == TRUE && result$floor_reached < 52)){
      watcher_list[result$play_id] = list(result)
    }
  }
}
cat(sprintf("%s total Watcher runs\n",length(watcher_list)))

```

## Group the data together (preliminary)

```{r, results="hide"}
#make table for each character with all the 1D attributes (will ignore other stuff for now)
onedim_cols = c("floor_reached","victory","killed_by","local_time","neow_cost","neow_bonus","campfire_rested","campfire_upgraded",
                "purchased_purges","player_experience","gold","playtime","seed_played","score","timestamp")

ironclad_tab = rbindlist(lapply(ironclad_list, function(x){
  x[onedim_cols]
}),fill=T)
silent_tab = rbindlist(lapply(silent_list, function(x){
  x[onedim_cols]
}),fill=T)
defect_tab = rbindlist(lapply(defect_list, function(x){
  x[onedim_cols]
}),fill=T)
watcher_tab = rbindlist(lapply(watcher_list, function(x){
  x[onedim_cols]
}),fill=T)

#sort with newest runs on top
ironclad_tab = ironclad_tab[order(timestamp,decreasing=T)]
silent_tab = silent_tab[order(timestamp,decreasing=T)]
defect_tab = defect_tab[order(timestamp,decreasing=T)]
watcher_tab = watcher_tab[order(timestamp,decreasing=T)]

#put them into one list
allchar_list = list("Ironclad"=ironclad_tab, "Silent"=silent_tab, "Defect"=defect_tab, "Watcher"=watcher_tab)
```

## For a first pass, I'm just going to output my overall winrate per character/rotating and my winrate per character/rotating over the last 25 and 50 runs

```{r}
char_vec = c("Ironclad","Silent","Defect","Watcher")
all_timestamps = c()
df = setNames(data.frame(matrix(ncol = 5, nrow = 3)), c(char_vec,"Rotating"))
rownames(df) = c("Overall","Last50","Last25")

for(char in char_vec){
  mychar_tab = allchar_list[[char]]
  all_timestamps = c(all_timestamps,mychar_tab[,timestamp])
  tot = nrow(mychar_tab)
  win_all = sum(mychar_tab[,victory])/tot
  win_50 = sum(mychar_tab[,victory][1:min(50,tot)])/min(50,tot)
  win_25 = sum(mychar_tab[,victory][1:min(25,tot)])/min(25,tot)
  df[char] = c(win_all,win_50,win_25)
}

#get rotating stats
all_timestamps = sort(all_timestamps,decreasing=T)
tot_curr = winsall_curr = wins50_curr = wins25_curr = 0

for(char in char_vec){
  mychar_tab = allchar_list[[char]]
  tot_curr = tot_curr + nrow(mychar_tab)
  winsall_curr = winsall_curr + sum(mychar_tab$victory)
  wins50_curr = wins50_curr + sum(mychar_tab[timestamp %in% all_timestamps[1:50]]$victory)
  wins25_curr = wins25_curr + sum(mychar_tab[timestamp %in% all_timestamps[1:25]]$victory)
}
df["Rotating"] = c(winsall_curr/tot_curr,wins50_curr/50,wins25_curr/25)

#save winrate stats over time
write.csv(df,file = file.path(my_working_dir,"winrate_history",paste0("winrate_",unlist(strsplit(as.character(Sys.time()), split=" "))[1],".csv")))

#plot this
plotdata = melt(data.table(df,keep.rownames = T),id.vars="rn")
colnames(plotdata) = c("Number of Runs","Character","Winrate")
plotdata$Winrate = plotdata$Winrate*100
plotdata$`Number of Runs` = factor(plotdata$`Number of Runs`,levels = c("Overall","Last50","Last25"),ordered=T)

p1 = ggplot(plotdata, aes(fill=`Number of Runs`, y=Winrate, x=Character)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("#7dcfb6", "#f79256", "#fbd1a2")) +
  ylab("Winrate (%)")

ggplotly(p1)
```

## Calculate current and max winstreaks

```{r}
curr_winstreaks = max_winstreaks = curr_lossstreaks = max_lossstreaks = vector("numeric")

#individual character winstreaks

for(char in char_vec){
  mychar_tab = allchar_list[[char]]
  mychar_tab = mychar_tab[order(timestamp,decreasing=T)]
  my_rle = rle(mychar_tab$victory)
  all_wins = my_rle$length[my_rle$values == TRUE]
  all_losses = my_rle$length[my_rle$values == FALSE]
  
  #get current streaks
  if(mychar_tab$victory[1]){ #if most recent run was a victory
    curr_winstreaks = append(curr_winstreaks,all_wins[1])
    curr_lossstreaks = append(curr_lossstreaks,0)
  }else{
    curr_winstreaks = append(curr_winstreaks,0)
    curr_lossstreaks = append(curr_lossstreaks,all_losses[1])
  }
  
  #get max streaks
  max_winstreaks = append(max_winstreaks, max(all_wins))
  max_lossstreaks = append(max_lossstreaks, max(all_losses))
}

#rotating winstreak, and determine which character i need to play next to continue rotating


```












